Decentralised Authoring, Annotations and Notifications for a Read-Write Web with dokieli

### 2017-04-07 index.tex
minor

\par \textbf{Accessibility}: To lower the barrier for entry for all forms of participation, enhanced functionality should be accessible to users based on the capabilities of their user-agents, storage availability, network access or personal preferences (we consider this to be self-evident, and there are a plethora of Web best practices in this area).

\par \textbf{Freedom of expression}: Because there are no central authorities, we must assume applications follow the open-world principle, where ``any author can say anything about anything''. Identifying everything using [de]referenceable IRIs allows any distributed authoring or annotation application to reference and link to previously published content (this overlaps with Principles 1, 3 and 4 in the \textit{W3C Semantic Web Activity}~\cite{ref-4} charter.

>>>>

\par \textbf{Accessibility}: To lower the entry barrier for all forms of participation, enhanced functionality should be accessible to users based on the capabilities of their user-agents, storage availability, network access or personal preferences (we consider this to be self-evident, and there are a plethora of Web best practices in this area).

\par \textbf{Freedom of expression}: Because there are no central authorities, we must assume applications follow the open-world principle, where ``any author can say anything about anything''. Identifying everything using [de]referenceable IRIs allows any distributed authoring or annotation application to reference and link to previously published content (this overlaps with Principles 1, 3 and 4 in the \textit{W3C Semantic Web Activity}~\cite{ref-4} charter).
